\subsubsection{Simple User Interface}
The user interface has to be as simple and intuitive as possible, the application should allow an average user to set up an account and start using the application understanding its functionality in no more than a dozen minutes. This application must be designed for all range of users and it must be suitable for people have disabilities. In addition there should be a complete tutorial to make it easy using the application.
\\

\subsubsection{Reliability}
The application provides a reliable service in which individual users can easily log in and go to a line up or book a visit in the most optimal way. Furthermore, it warranties that the chain of custody of the information coming from the users is never broken, and the information is never altered. This would provide a secure and reliable system.

\subsubsection{Availability}
The application must offer availability in the order of 99\% granting with in 8am-8pm(most of shops works in this hours). The lack of service must be minimal. It's better to better to maintain system at nights because people mostly do not use this application at night and many shops are closed. Even at night, we could put some resources at sleep mode to reduce the cost of application.
\\

\subsubsection{Security}
The users' location is a very important data and must be encrypted so this part must be more secure than other data stores in the application. Moreover, in case of password recovery this should never be sent in clear. The system must be behind a proxy servers (like cloudflare) to prevent the DDoS attacks.
\\

\subsubsection{Maintainability}
The application must keep a service log in order to fix bugs more easily. The app should be developed using a micro-service approach, so adding new functions shouldn’t require to change the previous code, and we can have different instance of services in different time of day. This application needs infrastructure like kubernetes to orchestrate the containers.
\\

\subsubsection{Portability}
The user side must be available in different platform like Android, IOS and Web. The backend side must be deployed with docker to easily deploy on any server.
\\

\subsubsection{Scalability}
Because this application is very useful to citizens and now it's a pandemic and people tend to be in home and not in the long lines, so many people will use this app and many managers add their shops in this app thus, so the system must have a good infrastructure which could balance the loads and easily we must add new resources to it.
\\